Missing The Point

### 2020-09-21 Manuscript.Rmd
Simulation results with data generation in each run (n_sim = 100)
rerun sim after feedback mice meeting that coverages are off

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results_standard_ci.Rdata")

@@

Missing data poses a ubiquitous threat against unbiased, confidence-valid statistical inferences. A popular tool to accommodate missing data. With techniques like multiple imputation (Rubin, 1987), missing data points are imputed (i.e., 'filled in')

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results.Rdata")

@@

Missing data poses a ubiquitous threat against unbiased, confidence-valid statistical inferences. A popular tool to accommodate missing data is iterative imputation. With techniques like multiple imputation (Rubin, 1987), missing data points are imputed (i.e., 'filled in')
